Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-13 paper/main.tex
added a paragraph about event boundaries (within list) to the results section.  also starting to write up indiivdual differences results...

\caption{\textbf{Recall dynamics in feature rich free recall (order
manipulation conditions).} \textbf{A.} Behavioral plots. \textbf{Left panels.}
The probabilities of initiating recall with each word are plotted as a function
of presentation position. \textbf{Middle panels.} The conditional probabilities
of recalling each word are plotted as a function of the relative position (Lag)
to the words recalled just-prior. \textbf{Right panels.} The overall
probabilities of recalling each word are plotted as a function of presentation
position. \textbf{All panels.} Error ribbons denote bootstrap-estimated 95\%
confidence intervals (calculated across participants). Top panels display the
recall dynamics for early (order manipulation) lists in each condition (color).
Bottom panels display the recall dynamics for late (randomly ordered) lists.
See Figures~\dynamicsRandom~and~\dynamicsAdaptive~for analogous plots for the
random (control) and adaptive conditions. \textbf{B.} Proportion of event
boundaries (see \textit{Methods}) for each condition's feature of focus,
plotted as a function of presentation position.}

@@

(Figs.~\ref{fig:recall-dynamics}, \ref{fig:fingerprints}). First, most of the

@@

@@

@@

% figure: feature clustering vs. accuracy, feature clustering vs. temporal clustering
\begin{figure}[tp] \centering
\includegraphics[width=\textwidth]{figures/feature_clustering_vs_accuracy_and_contiguity}

>>>>

\caption{\textbf{Recall dynamics in feature rich free recall (order
manipulation conditions).} \textbf{A.} Behavioral plots. \textbf{Left panels.}
The probabilities of initiating recall with each word are plotted as a function
of presentation position. \textbf{Middle panels.} The conditional probabilities
of recalling each word are plotted as a function of the relative position (Lag)
to the words recalled just-prior. \textbf{Right panels.} The overall
probabilities of recalling each word are plotted as a function of presentation
position. \textbf{All panels.} Error ribbons denote bootstrap-estimated 95\%
confidence intervals (calculated across participants). Top panels display the
recall dynamics for early (order manipulation) lists in each condition (color).
Bottom panels display the recall dynamics for late (randomly ordered) lists.
See Figures~\dynamicsRandom~and~\dynamicsAdaptive~for analogous plots for the
random (control) and adaptive conditions. \textbf{B.} Proportion of event
boundaries (see \textit{Identifying event boundaries}) for each condition's
feature of focus, plotted as a function of presentation position.}

@@

(Figs.~\ref{fig:recall-dynamics}A, \ref{fig:fingerprints}). First, most of the

@@

When we closely examined the sequences of words participants recalled in early
order manipulated lists (Fig.~\ref{fig:recall-dynamics}A, top panel), we
noticed several differences from the dynamics of participants' recalls of
randomly ordered lists (Fig.~\dynamicsRandom). One striking difference is that
participants in the category condition (dark purple curves,
Fig.~\ref{fig:recall-dynamics}) most often initiated recall with the
fourth-from-last item (\textit{Recall initiation}, top left panel), whereas
participants who recalled randomly ordered lists tended to initiate recall with
either the first or last list items (Fig.~\dynamicsRandom, top left panel). We
hypothesized that the participants might be ``clumping'' their recalls into
groups of items that shared category labels. Indeed, when we compared the
positions of feature changes in the study sequence
(Fig.~\ref{fig:recall-dynamics}B; see \textit{Identifying event boundaries})
with the positions of items participants recalled first, we noticed a striking
correspondence in both semantic conditions. Specifically, on category-ordered
lists, the category labels changed every four items on average (dark purple
peaks in Fig.~\ref{fig:recall-dynamics}B), and participants also seemed to
display an increased tendency (relative to other order manipulation and random
conditions) to initiate recall of category-ordered lists with items whose study
positions were integer multiples of four. Similarly, for size-ordered lists,
the size labels changed every eight items on average (light purple peaks in
Fig.~\ref{fig:recall-dynamics}B), and participants also seemed to display an
icnreased tendancy to initiate recall of size-ordered lists with items whose
study positions were integer multiples of eight. A second striking difference
is that participants in the category condition exhibited a much steeper lag-CRP
(Fig.~\ref{fig:recall-dynamics}A, top middle panel) than participants in other
conditions. (This is another expression of participants' increased tendencies
to temporally cluster their recalls on category-ordered lists, as we reported
above.) Taken together, these order-specific idiosyncracies suggest a
hierarchical set of influences on participants' memories. At longer timescales,
``event boundaries'' (to use the term loosely) can be induced across lists by
adding or removing irrelevant visual features. At shorter timescales, ``event
boundaries'' can be induced across items (within a single list) by adjusting
how item features change throughout the list.

@@

\begin{figure}[tp] \centering
    \includegraphics[width=\textwidth]{figures/feature_clustering_vs_accuracy_and_contiguity}

When we examined the data at the level of individual participants
(Fig.~\ref{fig:clustering-scatterplots}), a clearer story emerged.

@@

% figure: feature clustering vs. accuracy, feature clustering vs. temporal clustering
